Tampering Detection In Low-Power Smart Cameras

### 2015-05-26 paper.tex
Inserite reference su weighted kmeans

\gi{Qui ST pu\'o aggiungere qualche esempio di applicazione qui o menzionare dispositivi di riferimento (con tanto di link a datasheet). Magari aggiungendo che le batterie recenti permettono operativit\'a di due anni a questi regimi.}\cl{Verifico cosa possiamo dire del SecSoc.}
%
In this work we expressly target low-power and ultra-low-power smart cameras, devices that operate at very low frame-rates (e.g. possibly less than one frame every minute), that are characterized by a constrained computational power and memory, and that are battery powered (typically lasting one or two years). As an example, consider Wireless Multimedia Sensor Networks (WMSN) \cite{akyildiz2007survey} where nodes are wirelessy connected smart-cameras, that can acquire and transmit images at regular time interval or upon requests. Often, in WMSN, the units are not connected to the power supply and have to operate with batteries and possibly rely on energy harvesting mechanisms~\gi{REFERENCES, Adriano, guarda se c'e' qualche reference dal nostro paper di TIM}. Therefore, the power consumption is a serious concern in these devices.

@@

%What are the key components of my approach and results? Also include any specific limitations.
We present an algorithm to detect both camera defocus and displacement, as stated in Section \ref{sec:probForm}. The algorithm presented in Section~\ref{sec:Algorithm} relies on two indicators: the average image intensity to detect displacement, and the average gradient norm, to detect blur. These indicators can be easily computed and monitored by an outlier-detection technique to detect the respective tampering. We show that displacement-detection performance can be improved by means of a preliminarily partitioning of the scene into nonoverlapping regions, and then separately computing and monitoring the average intensity over different regions (Section \ref{subsec:Segmentation}). Remarkably, these regions need to be defined during an initial configuration phase of the smart camera, thus there is no relevant computational overhead w.r.t. monitoring the whole image. Experiments in Section \ref{sec:experiments} show that operating on image regions can substantially improve the detection of camera displacements. Concluding remarks and discussions are given in Section \ref{sec:Conclusion}.

@@

\subsection{Related Works}\label{subsec:relWorks}
% Why hasn't it been solved before? (Or, what's wrong with previous proposed solutions? How does mine differ?)
The literature concerning tampering detection is mostly focused on video surveillance applications and operates at few frames per second \gi{Adriano, \'e vero?}. Background models are typically leveraged to identify defocus and occlusions; in particular  ~\cite{aksay2007camera} performs detect defocus by analyzing the wavelet domain of each frame and performs histogram comparison for detecting occlusions, while camera displacements are not considered. A background-subtraction technique is employed in~\cite{saglam2009real} to identify defocus, occlusions, and displacements. \gi{FIXME Comparison in the Fourier domain for defocus detection, histogram comparison for occlusion detection, comparison between current background and delayed background for displacement detection}. Background subtraction is also used in \cite{gil2007automatic} to detect defocus, occlusions, and displacements. \gi{FIXME Comparison of edges pixels count for defocus detection, entropy comparison for occlusion detection, block matching algorithm for displacement detection}.
In contrast, no background models are used in \cite{alippi2010detecting}, where a sequential monitoring scheme based on a change-detection test is employed to detect changes in the average gradient energy of each frame to detect defocus due to external disturbances on the camera lens.  
\cite{ribnick2006real}: comparison between frames belonging to a buffer in order to find high values of dissimilarity, associated to tampering.
\cite{kryjak2012fpga}: implementation in a FPGA of a solution based on background modeling, histograms comparisons, edges comparisons.
\cite{harasse2004automated}: tampering detection inside a moving vehicle; uses background subtraction methods in order to identify defocus, occlusions, and displacements. Comparison of edges pixels count for defocus detection, entropy comparison for occlusion detection, block matching algorithm for displacement detection.
\cite{tsesmelis2013tamper}: monitoring of the number of key points extracted by SURF in order to detect defocus events, partition in blocks and HOG descriptors matching for each block in order to detect occlusions. These types of solutions requires a lot of computations
%
%
%
\section{Problem Formulation}\label{sec:probForm}
%
Let $z_t$ be the frame acquired at time $t$, which we model as
\begin{equation}
\label{eq:observationModel}
z_t(x)=\mathcal{D}_t[y_t](x) \quad \forall x \in X
\end{equation}
where $\mathcal{D}_t$ denotes the degradation operator that transforms the original image $y_t$ in the frame $z_t$; $X \subset \mathbb{Z}^2$ denotes the regular pixels grid and $x\in \mathbb{Z}^2$ indicates the pixel coordinates. As far as there is no tampering attacks/events,
\begin{equation}
\label{eq:no_tampering}
\mathcal{D}_t[y_t](x) = y_t(x) + \eta_t(x) \quad \forall x \in X
\end{equation}
where $\eta_t$ is a random variable accounting for different noise sources (e.g., thermal, quantization, photon-counting). In normal conditions, all the images $y_t$ (thus also the frames $z_t$) might show different content but are acquired from the same viewpoint and the same camera orientation.

@@

\subsection{Scene Segmentation}\label{subsec:Segmentation}
Consideriamo la sequenza $\{z_t\}$ di frame acquisiti dalla camera, con $t=1,\dots,T_{c}$.
Per ciascun pixel $x\in\mathcal{X}$ calcoliamo un vettore $\textbf{d}(x)$ di $5$ elementi
\begin{equation}
\label{eq:featureVector}
\textbf{d}(x)=\left[r(x);c(x);\mu_{\nabla}(x);\sigma_{\nabla}(x);\bar{z}(x)\right], \textbf{d}(x) \in \mathbb{R}^5
\end{equation}
dove:
\begin{itemize}
	\item $r(x)$ rappresenta il numero di riga del pixel $x$.
	\item $c(x)$ rappresenta il numero di colonna del pixel $x$.
	\item $\mu_{\nabla}(x)$ rappresenta il valore del gradiente nel pixel $x$ mediato nel tempo:
	\begin{equation}
	\label{eq:segmentazioneGrad}
	\mu_{\nabla}(x) = \frac{\sum_{t=1}^{T_c}(\|\nabla z_t\|_2^2 \circledast f)(x)}{T_c},
	\end{equation}
	dove abbiamo indicato con $\|\nabla z_t\|_2^2$ la norma del gradiente per l'immagine $z_t$, definita in \eqref{eq:normaGradiente}, e con $f$ il filtro gaussiano discreto derivato dal campionamento di \eqref{eq:gaussian}.
	\item $\sigma_{\nabla}(x)$ rappresenta la deviazione standard nel tempo del gradiente nel pixel $x$:
	\begin{equation}
	\label{eq:segmentazioneVar}
	\sigma_{\nabla}(x)=\sqrt{\frac{1}{T_c - 1}\sum_{t=1}^{T_c}\left(\left(\|\nabla z_t\|_2^2 \circledast f\right)(x)-\mu_{\nabla}(x)\right)^2}.
	\end{equation}
	\item $\bar{z}(x)$ rappresenta il valore della luma del pixel $x$ mediato nel tempo:
	\begin{equation}
	\label{eq:segmentazioneLuma}
	\bar{z}(x)=\frac{\sum_{t=1}^{T_c}( z_t \circledast f)(x)}{T_c}.
	\end{equation}
\end{itemize}
%
%
%
\subsection{Indicators}\label{subsec:Indicators}

@@

The algorithm uses low computational techniques: the biggest effort is made by computation of the feature $g(t)$, which needs $34$ operations per pixel, due to the Sobel filter used during the convolution.

>>>>

\gi{Qui ST pu\'o aggiungere qualche esempio di applicazione qui o menzionare dispositivi di riferimento (con tanto di link a datasheet). Magari aggiungendo che le batterie recenti permettono operativit\'a di due anni a questi regimi.}\cl{Verifico cosa possiamo dire del SecSoc.}
%
In this work we expressly target low-power and ultra-low-power smart cameras, devices that operate at very low frame-rates (e.g. possibly less than one frame every minute), that are characterized by a constrained computational power and memory, and that are battery powered (typically lasting one or two years). As an example, consider Wireless Multimedia Sensor Networks (WMSN) \cite{akyildiz2007survey} where nodes are wirelessy connected smart-cameras, that can acquire and transmit images at regular time interval or upon requests. Often, in WMSN, the units are not connected to the power supply and have to operate with batteries and possibly rely on energy harvesting mechanisms~\gi{REFERENCES, Adriano, guarda se c'e' qualche reference dal nostro paper di TIM} \cite{magno2009adaptive}. Therefore, the power consumption is a serious concern in these devices.

@@

%What are the key components of my approach and results? Also include any specific limitations.
We present an algorithm to detect both camera defocus and displacement, as stated in Section \ref{sec:probForm}. The algorithm presented in Section~\ref{sec:propSol} relies on two indicators: the average image intensity to detect displacement, and the average gradient norm, to detect blur. These indicators can be easily computed and monitored by an outlier-detection technique to detect the respective tampering. We show that displacement-detection performance can be improved by means of a preliminarily partitioning of the scene into nonoverlapping regions, and then separately computing and monitoring the average intensity over different regions (Section \ref{subsec:Segmentation}). Remarkably, these regions need to be defined during an initial configuration phase of the smart camera, thus there is no relevant computational overhead w.r.t. monitoring the whole image. Experiments in Section \ref{sec:experiments} show that operating on image regions can substantially improve the detection of camera displacements. Concluding remarks and discussions are given in Section \ref{sec:Conclusion}.

@@

\subsection{Related Works}\label{subsec:relWorks}
% Why hasn't it been solved before? (Or, what's wrong with previous proposed solutions? How does mine differ?)
The literature concerning tampering detection is mostly focused on video surveillance applications and operates at few frames per second \gi{Adriano, \'e vero?}. Background models are typically leveraged to identify defocus and occlusions; in particular  ~\cite{aksay2007camera} performs detect defocus \ad{defocus detection?} by analyzing the wavelet domain of each frame and performs histogram comparison for detecting occlusions, while camera displacements are not considered. A background-subtraction technique is employed in~\cite{saglam2009real} to identify defocus, occlusions, and displacements. \gi{FIXME Comparison in the Fourier domain for defocus detection, histogram comparison for occlusion detection, comparison between current background and delayed background for displacement detection}. Background subtraction is also used in \cite{gil2007automatic} to detect defocus, occlusions, and displacements. \gi{FIXME Comparison of edges pixels count for defocus detection, entropy comparison for occlusion detection, block matching algorithm for displacement detection}.
In contrast, no background models are used in \cite{alippi2010detecting}, where a sequential monitoring scheme based on a change-detection test is employed to detect changes in the average gradient energy of each frame to detect defocus due to external disturbances on the camera lens.  
\cite{ribnick2006real}: comparison between frames belonging to a buffer in order to find high values of dissimilarity, associated to tampering.
\cite{kryjak2012fpga}: implementation in a FPGA of a solution based on background modeling, histograms comparisons, edges comparisons.
\cite{harasse2004automated}: tampering detection inside a moving vehicle; uses background subtraction methods in order to identify defocus, occlusions, and displacements. Comparison of edges pixels count for defocus detection, entropy comparison for occlusion detection, block matching algorithm for displacement detection.
\cite{tsesmelis2013tamper}: monitoring of the number of key points extracted by SURF in order to detect defocus events, partition in blocks and HOG descriptors matching for each block in order to detect occlusions. These types of solutions requires a lot of computations
%
%
%
\section{Problem Formulation}\label{sec:probForm}
%
Let $z_t$ be the frame acquired at time $t$, which we model as
\begin{equation}
\label{eq:observationModel}
z_t(x)=\mathcal{D}_t[y_t](x) \quad \forall x \in X
\end{equation}
where $\mathcal{D}_t$ denotes the degradation operator that transforms the original image $y_t$ in the frame $z_t$; $X \subset \mathbb{Z}^2$ denotes the regular pixels grid and $x\in \mathbb{Z}^2$ indicates the pixel coordinates. As far as there is no tampering attacks/events,
\begin{equation}
\label{eq:no_tampering}
\mathcal{D}_t[y_t](x) = y_t(x) + \eta_t(x) \quad \forall x \in X
\end{equation}
where $\eta_t$ is a random variable accounting for different noise sources (e.g., thermal, quantization, photon-counting). In normal conditions, all the images $y_t$ (thus also the frames $z_t$) might show different content but are acquired from the same viewpoint and the same camera orientation.

@@

\subsection{Scene Segmentation}\label{subsec:Segmentation}
Consideriamo la sequenza $\{z_t\}$ di frame acquisiti dalla camera, con $t=1,\dots,T_{c}$.
Per ciascun pixel $x\in\mathcal{X}$ calcoliamo un vettore $\textbf{d}(x)$ di $5$ elementi
\begin{equation}
\label{eq:featureVector}
\textbf{d}(x)=\left[r(x);c(x);\mu_{\nabla}(x);\sigma_{\nabla}(x);\bar{z}(x)\right], \textbf{d}(x) \in \mathbb{R}^5
\end{equation}
dove:
\begin{itemize}
	\item $r(x)$ rappresenta il numero di riga del pixel $x$.
	\item $c(x)$ rappresenta il numero di colonna del pixel $x$.
	\item $\mu_{\nabla}(x)$ rappresenta il valore del gradiente nel pixel $x$ mediato nel tempo:
	\begin{equation}
	\label{eq:segmentazioneGrad}
	\mu_{\nabla}(x) = \frac{\sum_{t=1}^{T_c}(\|\nabla z_t\|_2^2 \circledast f)(x)}{T_c},
	\end{equation}
	dove abbiamo indicato con $\|\nabla z_t\|_2^2$ la norma del gradiente per l'immagine $z_t$, definita in \eqref{eq:normaGradiente}, e con $f$ il filtro gaussiano discreto derivato dal campionamento di \eqref{eq:gaussian}.
	\item $\sigma_{\nabla}(x)$ rappresenta la deviazione standard nel tempo del gradiente nel pixel $x$:
	\begin{equation}
	\label{eq:segmentazioneVar}
	\sigma_{\nabla}(x)=\sqrt{\frac{1}{T_c - 1}\sum_{t=1}^{T_c}\left(\left(\|\nabla z_t\|_2^2 \circledast f\right)(x)-\mu_{\nabla}(x)\right)^2}.
	\end{equation}
	\item $\bar{z}(x)$ rappresenta il valore della luma del pixel $x$ mediato nel tempo:
	\begin{equation}
	\label{eq:segmentazioneLuma}
	\bar{z}(x)=\frac{\sum_{t=1}^{T_c}( z_t \circledast f)(x)}{T_c}.
	\end{equation}
\end{itemize}

When the feature vectors are computed for all the pixels we start the segmentation phase.
This is made using classical clustering techniques:
in particular we use a modified version of the classical k-means algorithm \cite{han2006data}. 
In this implementation, each feature vector belongs to a cluster if its \textit{weighted Minkowski distance} \cite{de2012minkowski} from the cluster's centroid is minimum with respect to the distance from the other centroids. 
The distance is weighted considering the standard deviation of each elements of the feature vectors inside each cluster \cite{kottke1994motion}, in order to consider, during the clustering, also the contribute of the fields which have low variance. \ad{Giacomo: prova a vedere se si capisce cosa voglio dire in queste frasi!!!}

\subsection{Indicators}\label{subsec:Indicators}

@@

The algorithm uses low computational techniques: the biggest effort is made by computation of the feature $g(t)$, which needs $34$ operations per pixel, due to the Sobel filter used during the convolution.
The computational load could decrease using Fast Fourier Transform (FFT) \cite{brigham1988fast} and operating in the frequency domain.
